An Early Eocene temperature gradient modelled with geological and ecological proxies

### 2022-10-07 manuscript/manuscript.Rmd
test commit

**Coral reefs.** Coral reefs built by zooxanthellate-bearing, shallow water corals are confined to the tropics - substropics. The coldest

@@

## Model validation
- Show that the modern gradient can be reproduced with Eocene sampling distribution
[Fig 3 - Modern gradient]

>>>>

**Coral reefs.** Today, shallow warm-water coral reefs are restricted to tropical-to-subtropical latitudes.
Coral reefs built by zooxanthellate-bearing, shallow water corals are confined to the tropics - substropics. The coldest

@@

## Model validation
- Show that the 4-parameter logistic function can adequatly describe the modern temperature gradient
- Show that the modern gradient can be reproduced with Eocene sampling distribution
[Fig 3 - Modern gradient]

The average modern temperature gradient can be closely approximated with our model when using the full modern SST dataset (Fig. 3a). Degrading the amount and distribution of data points to match the early Eocene sampling distribution still results in a close match of the modelled gradient with the empirical gradient (Fig 3b). A noticable, but minor offset is apparent in high latitudes, where sampling is most incomplete (Fig 3b).
